To be FAIR: Theory Specification Needs an Update

### 2025-06-07 test.Rmd
manuscript.rmd not working, try test.rmd instead

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Aaron Peikert"
    affiliation: "2,3"
    role:
      - Conceptualization
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Maximilian S. Ernst"
    affiliation: "2,4"
    role:
      - Writing – review & editing
      - Investigation
  - name: "Noah N.N. van Dongen"
    affiliation: "5"
    role:
      - Writing – review & editing
  - name: "Felix D. Schönbrodt"
    affiliation: "6"
    role:
      - Conceptualization
      - Writing – review & editing
  - name: "Andreas M. Brandmaier"
    affiliation: "2,3,7"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Tilburg University department of Methodology & Statistics, Tilburg, The Netherlands"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
  - id            : "5"
    institution   : "University of Amsterdam, Amsterdam, The Netherlands"
  - id            : "6"
    institution   : "Ludwig-Maximilians-Universität München, München, Germany"
  - id            : "7"
    institution   : "MSB Medical School Berlin Department of Psychology, Berlin, Germany"
authornote: |
  We are particularly endebted to our Reviewer, Dr. Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion. We also thank the Editor, Dr. Scott Vrieze, and two anonymous Reviewers for their detailed and invaluable comments. This version of the paper was generated from Git Commit # `r substr(gert::git_commit_id(),1,8)`. The first and senior author positions were fixed, and remaining author positions randomized using `set.seed(6999982); sample(c("Aaron", "Felix", "Noah", "Maximilian"))`.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.md'))))`"
keywords          : "fairtheory, meta science, theory formation, open science"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')))`"
bibliography      : "fair_theory.bib"
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, noextraspace"
urlcolor          : blue
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            :
  papaja::apa6_pdf: default
  md_document: default
header-includes:
  - \usepackage{longtable, setspace, subfig}
  - \raggedbottom
---

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing - original draft
      - Writing – review & editing
  - name: "Aaron Peikert"
    affiliation: "2,3"
    role:
      - Conceptualization
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Maximilian S. Ernst"
    affiliation: "2,4"
    role:
      - Writing – review & editing
      - Investigation
  - name: "Noah N.N. van Dongen"
    affiliation: "5"
    role:
      - Writing – review & editing
  - name: "Felix D. Schönbrodt"
    affiliation: "6"
    role:
      - Conceptualization
      - Writing – review & editing
  - name: "Andreas M. Brandmaier"
    affiliation: "2,3,7"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Tilburg University department of Methodology & Statistics, Tilburg, The Netherlands"
  - id            : "2"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "3"
    institution   : "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany"
  - id            : "4"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
  - id            : "5"
    institution   : "University of Amsterdam, Amsterdam, The Netherlands"
  - id            : "6"
    institution   : "Ludwig-Maximilians-Universität München, München, Germany"
  - id            : "7"
    institution   : "MSB Medical School Berlin Department of Psychology, Berlin, Germany"

authornote: |
  We are particularly endebted to our Reviewer, Dr. Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion. We also thank the Editor, Dr. Scott Vrieze, and two anonymous Reviewers for their detailed and invaluable comments. This version of the paper was generated from Git Commit # `r substr(gert::git_commit_id(),1,8)`. The first and senior author positions were fixed, and remaining author positions randomized using `set.seed(6999982); sample(c("Aaron", "Felix", "Noah", "Maximilian"))`.

abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.md'))))`"

keywords          : "fairtheory, meta science, theory formation, open science"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')))`"
bibliography      : "fair_theory.bib"

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, noextraspace"

urlcolor          : blue
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            :
  papaja::apa6_pdf: default
  md_document: default
header-includes:
  - \usepackage{longtable, setspace, subfig}
  - \raggedbottom
---

### 2025-06-07 test.tex
manuscript.rmd not working, try test.rmd instead

We are particularly endebted to our Reviewer, Dr.~Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion. We also thank the Editor, Dr.~Scott Vrieze, and two anonymous Reviewers for their detailed and invaluable comments.

The authors made the following contributions. Caspar J. Van Lissa: Conceptualization, Formal Analysis, Funding acquisition, Methodology, Project administration, Software, Supervision, Writing -- original draft, Writing -- review \& editing; Aaron Peikert: Conceptualization, Formal Analysis, Writing -- original draft, Writing -- review \& editing; Maximilian S. Ernst: Writing -- review \& editing, Investigation; Noah N.N. van Dongen: Writing -- review \& editing; Felix D. Schönbrodt: Conceptualization, Writing -- review \& editing; Andreas M. Brandmaier: Formal Analysis, Writing -- original draft, Writing -- review \& editing.

>>>>

We are particularly endebted to our Reviewer, Dr.~Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion. We also thank the Editor, Dr.~Scott Vrieze, and two anonymous Reviewers for their detailed and invaluable comments. This version of the paper was generated from Git Commit \# 0df377d6. The first and senior author positions were fixed, and remaining author positions randomized using \texttt{set.seed(6999982);\ sample(c("Aaron",\ "Felix",\ "Noah",\ "Maximilian"))}.

The authors made the following contributions. Caspar J. Van Lissa: Conceptualization, Formal Analysis, Funding acquisition, Methodology, Project administration, Software, Supervision, Writing - original draft, Writing -- review \& editing; Aaron Peikert: Conceptualization, Formal Analysis, Writing -- original draft, Writing -- review \& editing; Maximilian S. Ernst: Writing -- review \& editing, Investigation; Noah N.N. van Dongen: Writing -- review \& editing; Felix D. Schönbrodt: Conceptualization, Writing -- review \& editing; Andreas M. Brandmaier: Formal Analysis, Writing -- original draft, Writing -- review \& editing.
